---
title: "Outline of update step"
author: "JM Delgado"
date: "`r Sys.Date()`"
output:
  rmarkdown::github_document:
    toc: true
    toc_depth: 1
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Funceme data

## Reservoir level

1. get reservoir metadata from API (restrict query by federal state _uf_ i.e. _unidade federal_)
2. loop on all reservoirs selected to check for monitoring updates
3. publish alongside buhayra

### Reservoir metadata
```{r include=FALSE}
library(magrittr)
```
Trying to implement the following request `http://api.funceme.br/rest/acude/reservatorio?limit=10&page=3`
```{r results='asis'}

url='http://api.funceme.br'
path='rest/acude/reservatorio'
raw = httr::GET(url = url, path = path, query=list(limit='5',page='2'))

json_content=rawToChar(raw$content) %>%
  jsonlite::fromJSON()

```


## Precipitation

1. get gauge metadata from API
2. loop on all gauges
3. publish alongside buhayra

```{r include=FALSE}
source("/home/delgado/proj/valbuhayra/pw.R")
```

# TRMM data

# buhayra data
