---
title: "Outline of update step"
author: "JM Delgado"
date: "`r Sys.Date()`"
output:
  rmarkdown::github_document:
    toc: true
    toc_depth: 1
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Funceme data

## Reservoir level

1. get reservoir metadata from API (restrict query by federal state _uf_ i.e. _unidade federal_)
2. loop on all reservoirs selected to check for monitoring updates
3. publish alongside buhayra

### 1. Reservoir metadata

Trying to implement the following request `http://api.funceme.br/rest/acude/reservatorio?limit=10&page=3`

Obtain total number of pages:
```{r results='asis'}
library(dplyr)
library(sf)

url='http://api.funceme.br'
path='rest/acude/reservatorio'
raw = httr::GET(url = url, path = path)

json_content=rawToChar(raw$content) %>%
  jsonlite::fromJSON()

total_pages=json_content$paginator$page$total
```
Loop over total number of pages and save relevant reservoir metadata.
```{r results='asis'}
reservoirs_list=list()
for(page_i in seq(1,total_pages))
  {
    raw = httr::GET(url = url, path = path,
      query=list(page=paste0(page_i)))
    json_content=rawToChar(raw$content) %>%
      jsonlite::fromJSON()
    reservoirs_list[[page_i]]=json_content$list %>%
      select(cod,nome,municipio,longitude,latitude,capacidade,altura_maxima)
  }
reservoirs=do.call('rbind',reservoirs_list)
reservoirs = reservoirs %>%
  filter(!is.na(longitude) & !is.na(latitude)) %>%
  st_as_sf(coords=c('longitude','latitude'))
save(reservoirs,file='data/reservoirs.RData')
```

### 2. Loop and check for updates
Querying reservoir level looks like:

```{r results='asis'}
library(lubridate)
cod_i=1119

url='http://api.funceme.br'
path='rest/acude/volume'
cutoff_date=today()-7
raw = httr::GET(url = url, path = path,
  query=list(reservatorio.cod=paste0(cod_i),
  dataColeta.GTE=paste0(with_tz(cutoff_date,tz="America/Sao_Paulo")),
  orderBy='dataColeta,cres'))
  json_content=rawToChar(raw$content) %>%
    jsonlite::fromJSON()

volumes=json_content$list %>%
  select(dataColeta,valor,percentual) %>%
  mutate(cod=cod_i)
```

So an equivalent function should look like:

```{r results='asis'}
currentVolume <- function(cod_i) {
  url='http://api.funceme.br'
  path='rest/acude/volume'
  cutoff_date=today()-7
  raw = httr::GET(url = url, path = path,
    query=list(reservatorio.cod=paste0(cod_i),
    dataColeta.GTE=paste0(with_tz(cutoff_date,tz="America/Sao_Paulo")),
    orderBy='dataColeta,cres'))
    json_content=rawToChar(raw$content) %>%
      jsonlite::fromJSON()

    volumes=json_content$list %>%
      select(dataColeta,valor,percentual) %>%
      mutate(cod=cod_i)

    return(volumes)
}
```

## Precipitation

1. get gauge metadata from API
2. loop on all gauges
3. publish alongside buhayra

```{r include=FALSE}
source("/home/delgado/proj/valbuhayra/pw.R")
```

# TRMM data

# buhayra data
