---
title: "Outline of update step"
author: "JM Delgado"
date: "`r Sys.Date()`"
output:
  rmarkdown::github_document:
    toc: true
    toc_depth: 1
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Funceme data

## Reservoir level

1. get reservoir metadata from API (restrict query by federal state _uf_ i.e. _unidade federal_)
2. loop on all reservoirs selected to check for monitoring updates
3. publish alongside buhayra

### 1. Reservoir metadata

Trying to implement the following request `http://api.funceme.br/rest/acude/reservatorio?limit=10&page=3`

Obtain total number of pages:
```{r results='asis'}
library(dplyr)
library(sf)

url='http://api.funceme.br'
path='rest/acude/reservatorio'
raw = httr::GET(url = url, path = path,
  query=list(uf='23'))

json_content=rawToChar(raw$content) %>%
  jsonlite::fromJSON()

total_pages=json_content$paginator$page$total
```
Loop over total number of pages and save relevant reservoir metadata.
```{r results='asis'}
reservoirs=list()
for(page_i in seq(1,total_pages))
  {
    raw = httr::GET(url = url, path = path,
      query=list(uf='23',page=paste0(page_i)))
    json_content=rawToChar(raw$content) %>%
      jsonlite::fromJSON()
    reservoirs[[page_i]]=json_content$list %>%
      select(cod,nome,municipio,longitude,latitude)
  }
reservoirs=do.call('rbind',reservoirs)
reservoirs_meta = reservoirs %>%
  filter(!is.na(longitude) & !is.na(latitude)) %>%
  st_as_sf(coords=c('longitude','latitude'))
```

### 2. Loop and check for updates

```{r results='asis'}
```

## Precipitation

1. get gauge metadata from API
2. loop on all gauges
3. publish alongside buhayra

```{r include=FALSE}
source("/home/delgado/proj/valbuhayra/pw.R")
```

# TRMM data

# buhayra data
